\documentclass[10pt]{article}
\usepackage[top=1.0in, bottom = 1.0in, left = 1.0in , right = 1.0in]{geometry}

\usepackage{graphicx}
\usepackage{enumitem}

\usepackage[hidelinks]{hyperref} 
\usepackage{framed, color}
\definecolor{shadecolor}{gray}{0.9}
\usepackage{paralist}
\usepackage{color}
\usepackage{hyperref}



\usepackage{charter} %font matter


%	Template :: CV_IIIT-B_TEMPLATE
%	Credits	:: Sujit Kumar Muduli (MT2015113)
%


\newcommand{\shadethis}[1]{ \begin{snugshade}#1\end{snugshade}}

\newcommand{\myname}[1]
{
		\scalebox{1.5}{{{#1}}}\\
}

\newcommand{\degree}[2]{\emph{#1}\hspace{7cm}#2\\}
\newcommand{\inst}[2]{\textsf{#1}\qquad \qquad \qquad \scalebox{0.8}{CGPA} : #2}
\newcommand{\person}[5]
{
		\scalebox{1.5}{#1}\\
		26/C, IIIT-B, Hosur Road\\
		Electronic City - 1, Bangalore\\
		\Telefon : {+91-#3}\\
		\Mundus : \href{https://#5}{#5}\\
		\Letter : \href{mailto:#4@iiitb.org}{#4@iiitb.org}\\
		
}

\begin{document}
	
	
	\begin{center}
		\textbf{\Large Prachi Prakash Mahapatro}
		\begin{center}
			26/C, IIIT-B, Hosur Road \\
			Electronic City - 1, Bangalore \\
			Phone : \texttt{+91-7406410984}\\
			e-mail : \href{prachiprakash.mahapatro@iiitb.org}{\texttt{prachiprakash.mahapatro@iiitb.org}}\\
		\end{center} 

	\end{center}
	

	\begin{description}[style=nextline]
		
		\shadethis{\item{\scalebox{1.2}{\bf \textsc{Area of Interest}}}}
		
			Data Structures,  Algorithms, Information Retrieval, Operating Systems.
		
		\shadethis{\item{\scalebox{1.2}{\bf \textsc{Academic Details}}}}
			\begin{tabular}{p{2cm}|p{10cm}}
			{2015 - \emph{cont.}} & \textbf{Master of Technology} in Information Technology\\
			  		& \emph{International Institute of Information Technology}\\
					& Bangalore, Karnataka \\
					& {CGPA - 3.35/4.0 \emph{(till 2\textsuperscript{nd} semester)}} 
					
			\end{tabular}
			
			\begin{tabular}{p{2cm}|p{10cm}}

			{2009- 2013} 	& \textbf{Bachelor of Technology} in Computer Science \& Engineering \\
			 	& \emph{National Institue of Science \& Technology} \\
				& Berhampur, Odisha\\
				& {CGPA - 8.58/10.0}		
			\end{tabular}
		
		\begin{tabular}{p{2cm}|p{10cm}}

			{2007- 2009} 	& \textbf{+2} in Science \\
			 	& \emph{BA College} \\
				& Berhampur, Odisha\\
				& {Percentage - 63.8}		
			\end{tabular}
			
			\begin{tabular}{p{2cm}|p{10cm}}

			{2007} 	& \textbf{10th from} \\
			 	& \emph{St. Vincent's Convent School} \\
				& Berhampur, Odisha\\
				& {Percentage - 80.6}		
			\end{tabular}
			
		\shadethis{\item{\scalebox{1.2}{\bf \textsc{Work Experience}}}}
		\begin{tabular}{p{2cm}|p{10cm}}
			{ Jul 2016 - Aug 2016} & \textbf{Teaching assistantship} for Java Programming course for Mtech,2016 Batch
			  		
					  		
					
			\end{tabular}
			
			\begin{tabular}{p{2cm}|p{10cm}}
			{ Jun 2013 - May 2014} & \textbf{Software Engineer} Capgemini India Pvt. Ltd.
			  		
					
			\end{tabular}
		
		
		\shadethis{\item{\scalebox{1.2}{\bf \textsc{Projects Undertaken}}}}
		
				
			\begin{itemize}
				
				\item \textbf{Akshaya: latent Semantic Association Mining Using Cognitive Modelling}
				\begin{itemize}
					\item Improved the add pipeline for adding a document to the knowledge base.
					\item Implemented a semantic Association Mining Algorithm, Topical Marker.
					\item \emph{Programming Language} :  Ruby
					
				\end{itemize}
				
				
				{\emph{Guide} : Prof. Srinath Srinivas}\hfill(January, 2016 - May, 2016)
				
				\item \textbf{JSON Parser}
				\begin{itemize}
					\item Implemented a recursive descent parser for JSON Data.
					
					\item \emph{Programming Language} :  Java
					
				\end{itemize}
				
				
				\hfill(Jul, 2016 - Jul, 2016)
			
				
				
				
				\item \textbf{A Student Social Networking Solution for iiit-b }
				\begin{itemize}
					\item Designed the database for the System .
					\item  Implemented the features using MVC Architecture
					\item \emph{Technologies \& Tools}: mysql, Swing, MVC Pattern.
					\item \emph{Programming Language}:  Java
				\end{itemize}								
				\hfill(Jul, 2015 - Aug, 2015)
			
%\newpage
				
				\item \textbf{Veeva Support for Boehringer Ingelheim }
				\begin{itemize}
					\item Did this as part of Capgemini.
					\item Did User migration from sandbox to production for new county on boarding.
					\item Did Product Information migration from legacy system to Salesforce Veeva.
					\item \emph{Technologies \& Tools}: Salesforce (SaaS).
				\end{itemize}								
				\hfill(Sept, 2013 - May, 2014)
				
					\end{itemize}				
			
			
		\shadethis{\item{\scalebox{1.2}{\bf \textsc{Online Courses \& Certifications}}}}		
			\begin{itemize}
				\item \textbf{Text Retrieval and Search Engine} by  University of Illinois at Urbana-Champaign,Coursera,July 2016.
				
				\item\textbf{Hadoop Platform and Application Framework} UC San Diego, Coursera,May 2016.
				\item\textbf{Salesforce DEV 401 Certified},Nov 2013
				\item\textbf{IBM Certified}Rational Application Developer For WebSphere Software V6.0,Mar 2013 

				
			\end{itemize}	
			
%			\shadethis{\item{\scalebox{1.2}{\bf \textsc{Areas of Interest}}}}
%			\begin{compactitem}
%				\item Cryptography
%				\item Internet of Things	
%				\item Algorithm and Complexity Theory
%				%				\item Quantum Computing		
%			\end{compactitem}
			
						
		\shadethis{\item{\scalebox{1.2}{\bf \textsc{Computer Skills}}}}
		\begin{itemize}
			\item \textbf{Programming languages} : C , Java, Python(Working Proficiency), Ruby(Working Proficiency)
			\item \textbf{Software Packages} : Latex, git
			\item \textbf{OS Platforms} :	Linux, Windows
		\end{itemize}	
		
		\shadethis{\item{\scalebox{1.2}{\bf \textsc{Recent Achievements}}}}
		\begin{itemize}			
			
			
			\item 98.9 Percentile in CS paper of GATE - 2016.
			
			\item 98.9 Percentile in CS paper of GATE - 2015.
			
			\item Qualified the initial round  of IBM-TGMC 2013.
			
			\item Won C and Java Programming Competitions during undergraduate studies.
						
		\end{itemize}
		
		\shadethis{\item{\scalebox{1.2}{\bf \textsc{Personal Information}}}}
		\begin{tabular}{l c l}
			Date of Birth &:& August 7, 1990\\
			Nationality &:& Indian\\
			Languages Known &:& Odia(Native speaker), English, Hindi
		\end{tabular}
		
				
		
				
	\vspace*{3em}
	I hereby certify that all the above information stated in this resume is
	true and complete to the best of my knowledge.\\[0.1cm]
	\mbox{}\hfill Prachi Prakash Mahapatro
	\end{description}

\end{document}
